---
name: Ivan
surname: Plyushchenko
position: ""
address: ""
profilepic: ""
email: "plyushchenko.ivan@gmail.com"
github: plyush1993
www: orcid.org/0000-0003-3883-4695
date: "`r format(Sys.time(), '%B %Y')`"
docname: CV
output: 
  vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Doctor of Philosophy (Chemistry)", "2017-22", "Lomonosov Moscow State University", "Moscow, Russia",
   "Postgraduate academic and pedagogical training (Chemistry)", "2017-21", "Lomonosov Moscow State University", "Moscow, Russia",
  "Specialist in Chemistry (equivalent to MSc), GPA: 4.67", "2011-17", "Lomonosov Moscow State University", "Moscow, Russia"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Key Publications

```{r}
library(scholar)
library(stringr)
library(tibble)
library(ggthemes)
library(ggplot2)
id <- 'Mz4nxtwAAAAJ'
p1 <- get_publications(id)
ct <- get_citation_history(id)
y <- unique(p1[order(p1$year, decreasing = F),]$year)
p <- p1[,c(2, 1, 3, 6, 4, 5)]
p$cites <- paste0("[Citations: ", p$cites, "]")
p <- p[order(p$year, decreasing = T),]
p <- filter(p, journal %in% c("Analytical Methods", "Metabolites", 
                              "Analytical and Bioanalytical Chemistry", 
                              "Journal of Chromatography A", "Journal of Proteome Research"))
p %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

# Certificates

```{r}
library(tibble)
tribble(
  ~ Certificate, ~ Year, ~ Organization, ~ Hours, 
  "Data Science 201: Going Further With R: Tackling Clinical Laboratory Data Manipulation and Modeling", "2019", "The Association for Mass Spectrometry & Advances in the Clinical Lab (MSACL) Conference EU", "16 hrs",
  "Metabolomics 202: Approaches, Applications and Challenges", "2017", "The Association for Mass Spectrometry & Advances in the Clinical Lab (MSACL) Conference EU", "16 hrs"
) %>% 
  detailed_entries(Certificate, Year, Organization, Hours)
```

# Grants and awards

```{r}
library(tibble)
tribble(
  ~ Grant, ~ Year, ~ Role, ~ Time,
  "Russian Foundation for Basic Research", "2018-22", "Participant", "3 grants",
  "Russian Science Foundation", "2017-21", "Participant", "2 grants"
) %>% 
  detailed_entries(Grant, Year, Role, Time)
```

```{r}
library(tibble)
tribble(
  ~ Award, ~ Year, ~ Place,
  "Winner of the competition of works contributing to the solution of problems of the Development Program of Moscow State University in the nomination 'Outstanding scientific articles'", "2022", "Moscow, Russia",
  "Competition of the Russian Academy of Sciences of scientific works of young scientists in chromatography in honor of the 150th anniversary of the birth M.S. Tsvet", "2022", "Moscow, Russia",
  "The Association for Mass Spectrometry & Advances in the Clinical Lab (MSACL) Conference EU Travel Grant", "2019", "Salzburg, Austria",
  "International Mass Spectrometry Conference Fellowship", "2018", "Florence, Italy",
  "The Association for Mass Spectrometry & Advances in the Clinical Lab (MSACL) Conference EU Travel Grant", "2017", "Salzburg, Austria"
) %>% 
  detailed_entries(Award, Year, Place)
```

# Professional Experience

```{r}
library(tibble)
tribble(
  ~ Job, ~ Year, ~ Role,
  "Junior research associate", "2019-22", "Lomonosov Moscow State University",
  "Lab technician", "2016-19", "Lomonosov Moscow State University",
  "Analytical chemist", "2015-18", "Analytical centre of Lomonosov Moscow State University"
) %>% 
  detailed_entries(Job, Year, Role)
```

# Skills & proficiencies

Instruments & techniques:

- MS: SCAN, SIM, MRM, DDA, DIA, PASEF, TIMS
- LC: RP, HILIC
- Nano LC: Evosep One (Evosep)
- LC-MS: IT-TOF (Shimadzu); Orbitrap Exploris 120, Orbitrap Q Exactive (Thermo); QTRAP 3200 (Sciex); 6470 (Agilent); timsTOF Pro (Bruker)
- LC-DAD: 1100, 1200, 1290 Infinity (Agilent); Ultimate 3000 (Dionex); LC 20 (Shimadzu); Vanquish (Thermo)
- LC-FLD: 1200 (Agilent); Ultimate 3000 (Dionex)
- CE-UV: G1600AX, 7100 (Agilent)
- GC-MS: GCMS-QP 2010 with SHS (Shimadzu); 7890 B (Agilent)
- GC-FID: GC-2010 (Shimadzu)

Basic lab skills:

- Extraction from liquid & solid media
- SPE, LLE, Soxhlet extraction, centrifugation, membrane filtering
- UV/Vis analysis, pH measurement 
- Preparation of calibration curves, QC/QA programs performing, daily maintenance
- Cell culture maintenance

Programming, Software & Bioinformatics tools:

- R language independent user
- tidyverse, tidymass, RforMassSpectrometry families of packages
- xcms, CAMERA, IPO, MSnbase, MSstats, Biostrings, seqinr, rcdk, caret, H2O, keras, xgboost, ggplot2, dplyr, data.table, RMarkdown 
- tool development list: [URL](https://github.com/plyush1993?tab=repositories)
- full list of R packages that is used for metabolomics processing: [URL](https://github.com/plyush1993/OUKS/blob/main/Used%20packages.pdf)
- GUI software: MetaboAnalyst, MS-DIAL, MZmine, MS-FINDER, SIRIUS+CSI:FingerID, CFM-ID, MetFrag, GNPS, Open Babel, FragPipe, DIA-NN, Alphapept
- Vendor Software: LabSolutions (Shimadzu); XCalibur, FreeStyle, Compound Discoverer (Thermo); OpenLab, MassHunter, ChemStation (Agilent); Compass HyStar, OtofControl (Bruker)

```
```

# Teaching and mentorship

```{r}
library(tibble)
tribble(
  ~ Course, ~ Year,
  "Mentoring undergraduates students of Lomonosov
Moscow State University, Faculty of Chemistry, including two students' thesis supervision", "2018-22",
  "Practical and theoretical classes on analytical chemistry for students of Lomonosov
Moscow State University, Faculty of Biology", "2018-20",
"Agilent advanced training courses at the Analytical centre of Lomonosov Moscow State University in LC, LC-MS", "2016-19"
) %>% 
  detailed_entries(with = Course, what = Year)
```

# Current journal roles

```{r}
library(tibble)
tribble(
  ~ Journal, ~ Current_journal_roles,
  "Biomedical Chromatography", "Peer Reviewer",
  "Journal of Analytical Chemistry", "Peer Reviewer", 
  "BMC Medicine", "Peer Reviewer"
) %>% 
  detailed_entries(with = Current_journal_roles, what = Journal)
```

# Publication list

```{r}
library(scholar)
library(stringr)
library(tibble)
library(ggthemes)
library(ggplot2)
id <- 'Mz4nxtwAAAAJ'
p1 <- get_publications(id)
ct <- get_citation_history(id)
y <- unique(p1[order(p1$year, decreasing = F),]$year)
p <- p1[,c(2, 1, 3, 6, 4, 5)]
p$cites <- paste0("[Citations: ", p$cites, "]")
p <- p[order(p$year, decreasing = T),]
p %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

# Conferences

```{r}
library(tibble)
tribble(
  ~ Title, ~ Conference, ~ Date,
  "Untargeted urinary metabolomics for identification of bladder cancer biomarkers using HPLC-MS",
  "Euroanalysis XXI, Geneva, Switzerland", "2023",
  "Application of gradient boosting machine for signal processing in LC-MS metabolomics", 
  "13th Winter Symposium on Chemometrics, Russia", "2022",
  "Untargeted metabolomics study of Humulus lupulus brewing cultivars, for genetic origin classification task", 
  "13th Winter Symposium on Chemometrics, Russia", "2022",
  "Describing metabolome diversity between Humulus lupulus genetic origin groups using UHPLC-MS/MS", 
  "The 69th Annual Conference on Mass Spectrometry of MSSJ, Japan", "2021",
  "Humulus lupulus LC-MS untargeted profiling study for geographic origin classification task",
  "4th International Symposium on Phytochemicals in Medicine and Food, Xi'an, China", "2020",
  "Comparison of the kinetics of dyes degradation of handwritten strokes subjected to different types of artificial aging and studied using chromatography mass-spectrometry and statistical data processing", 
  "48th International Symposium on High-Performance Liquid Phase Separations and Related Techniques, Milan, Italy", "2019", 
  "Bioassay Classification Study via LC-MS and Machine Learning in Conjunction with Dimensionality Reduction", 
  "MSACL 2019 EU, Salzburg, Austria", "2019",
   "Typical LC-MS metabolomics workflow for profiling urine samples of patients with colorectal cancer", 
  "XXII International Mass Spectrometry Conference, Florence, Italy", "2018",
  "Simple & Robust Approach in Urinary Metabolomics Based on UPLC-MS for Preoperative Colorectal Cancer Diagnostics", "MSACL 2017 EU, Salzburg, Austria", "2017",
  "Complexation of sulfo-β-cyclodextrin with fenoterol. Electrophoretic and spectroscopic study", 
  "VIIIth International Symposium Design and Synthesis of Supramolecular Architectures, Kazan, Russia", "2016" 
) %>% 
  detailed_entries(with = Conference, what = Title, when = Date)
```
